Cartograms with Dynamic Features

### 2022-03-04 paper/GHRVis.tex
draft: EHR data description
draft: add algorithms
draft: update main section
draft: update
draft: update algorithm and review
draft: update and review
draft: latex structure change

% code listing
\usepackage{listings}
\lstdefinestyle{customc}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  xleftmargin=\parindent,
  language=C,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{green!40!black},
  commentstyle=\itshape\color{purple!40!black},
  identifierstyle=\color{blue},
  stringstyle=\color{orange},
}

\lstdefinestyle{customasm}{
  belowcaptionskip=1\baselineskip,
  xleftmargin=\parindent,
  language=[x86masm]Assembler,
  basicstyle=\footnotesize\ttfamily,
  commentstyle=\itshape\color{purple!40!black},
}

\lstset{escapechar=@,style=customc}

@@

@@

\title{GHRVis:}

@@

% auto labeling of sections
\let\origsection=\section
\renewcommand\section[1]{\origsection{#1}\label{sec:{#1}}}

\let\origsubsection=\subsection
\renewcommand\subsection[1]{\origsubsection{#1}\label{subsec:{#1}}}

\let\origsubsubsection=\subsubsection
\renewcommand\subsubsection[1]{\origsubsubsection{#1}\label{subsubsec:{#1}}}

\newcommand{\figureref}[1]{Figure \ref{#1}}
\newcommand{\tableref}[1]{Table \ref{#1}}
\newcommand{\phantomref}[1]{$\hyperref[#1]{\ref{#1}}$}

% Bob's dream paragraph style
\newcommand{\bobgraph}[1]{ \noindent\textbf{#1} \phantomsection \label{bobgraph:{#1}}}

\definecolor{Mycolor1}{HTML}{4C5866} %#4C5866
\definecolor{Mycolor2}{HTML}{A6B6D2} %#A6B6D2
\definecolor{Mycolor3}{HTML}{67daff} %#67daff
\definecolor{Mycolor4}{HTML}{F7F7FE} %#F7F7FE
\definecolor{Mycolor5}{HTML}{666ad1} %#666ad1
\definecolor{Mycolor6}{HTML}{ffbb93} %#ffbb93
\newcommand{\mycolorbox}[2]{\begingroup\setlength{\fboxsep}{2pt}\colorbox{#1}{#2}\endgroup}

% table cite
\newcommand{\citea}[1]{\citeauthor{#1}\cite{#1}}

% customized table headers
\newcommand{\theaderR}[1]{\multicolumn{1}{c|}{\cellcolor{Mycolor3} \textbf{\rotatebox{90}{#1 \phantom{-} }}}}
\newcommand{\theaderP}[1]{\cellcolor{Mycolor3} \textbf{#1}}

\newcommand{\note}[1]{\textcolor{blue}{#1}}

\newcommand{\expertcomment}[1]{\textit{``#1''}}

\newcommand{\task}[1]{\textbf{T#1}}
\newcommand{\req}[1]{\textbf{R#1}}

@@

\section{GHRVis}

\subsection{VPSC}

>>>>

@@

\usepackage{multicol}

\include{preamble/preamble.basic}
\include{preamble/preamble.main}
\include{preamble/preamble.math}
\include{preamble/preamble.draft}

@@

\title{Cartograms with Dynamic Features}

@@

@@

\input{section/main}

### 2022-03-04 paper/section/main.tex
draft: latex structure change

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth]{figure/flowchart.png}
    \caption{A flowchart abstraction of our layout algorithm.}
    \label{fig:flowchart}
\end{figure}
}

@@

    \textbf{Local variables:} \\
    $ \nodePrevious \gets $ the previous position of $ \node $ \\
    $ \PointP \gets $ the point extending $ \nodeVectorPC $ such that the length of $ \nodeLineNpP $ is $ \CorridorLength $\\
    $ \EdgeParallelA, \EdgeParallelB \gets $ the edges parallel to $ \nodeLineNpP $ \\
    $ corridor \gets $ a rectangle formed by $ \EdgeParallelA $ and $ \EdgeParallelB $ \\

>>>>

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth]{figure/flowchart.png}
    \caption{A flowchart showing the abstraction of our layout algorithm.}
    \label{fig:flowchart}
\end{figure}
}

@@

    \textbf{Local variables:} \\
    $ \nodePrevious \gets $ the previous position of $ \node $ \\
    $ \PointP \gets $ the point extending $ \nodeVectorPC $ such that $ \nodeLineWidthNpP = \CorridorLength $\\
    $ \EdgeParallelA, \EdgeParallelB \gets $ the edges parallel to $ \nodeLineNpP $ \\
    $ corridor \gets $ a rectangle formed by $ \EdgeParallelA $ and $ \EdgeParallelB $ \\

### 2022-03-04 paper/section/related.tex
draft: latex structure change

\citea{warf2008Geography} use a Dorling cartogram to represent the religious diversity in the United States. \citea{sun2010Effectiveness} depict 1996 US election data and 2005 Chinese population data using Dorling, Mosaic, and contiguous cartograms. \citea{gao2020Visualising} present a Dorling cartogram to illustrate COVID-19 infections in China. \citea{tong2018cartograms} use a Demers cartogram to visualize health-related data by CCG regions in England, the work introduces a novel technique to remove overlap of squares based on topological features, aiming to improve both geographical and topological accuracy. \citea{nusrat2020Recognition} investigate the memorability of contiguous and Dorling cartograms by using multiple datasets including demographics, agriculture, and retail data in the US. See Table \ref{table:region vs node} for a list of literature that adopts cartograms for visualization with corresponding geographical regions and node counts.

>>>>

\citea{warf2008Geography} use a Dorling cartogram to represent the religious diversity in the United States. \citea{sun2010Effectiveness} depict 1996 US election data and 2005 Chinese population data using Dorling, Mosaic, and contiguous cartograms. \citea{gao2020Visualising} present a Dorling cartogram to illustrate COVID-19 infections in China. \citea{tong2018cartograms} use a Demers cartogram to visualize health-related data by CCG regions in England, the work introduces a novel technique to remove overlap of squares based on topological features, aiming to improve both geographical and topological accuracy. \citea{nusrat2020Recognition} investigate the memorability of contiguous and Dorling cartograms by using multiple datasets including demographics, agriculture, and retail data in the US. See \tableref{table:region vs node} for a list of literature that adopts cartograms for visualization with corresponding geographical regions and node counts.
